### 2010-06-14 code/subarchitectures/visualization.sa/trunk/doc/v11n.tex
v11n: docs

@@

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   DispList:create(name)
   DispList:replace(name)
   DispList:endList()
   DispList:delete(name)
   DispList:exists(name)
   DispList:draw(name)
\end{Verbatim}

@@

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   function make_the_thing()
      DispList:create('myobject')
        glBegin(GL_TRIANGLES)
        glVertex(0.1, 0.1, 0.1)
        glVertex(0.3, 0.1, 0.2)
        glVertex(0.3, 0.4, 0.3)
        glEnd()
      DispList:endList()
   end

   function initlists()
      if not DispList:exists('myobject') then
         make_the_thing()
      end
   end

@@

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   function make_the_thing()
      DispList:create('myobject')
        glBegin(GL_QUADS)
        glVertex(0.1, 0.1, 0.1)
        glVertex(0.3, 0.1, 0.2)
        glVertex(0.3, 0.4, 0.3)
        glVertex(0.0, 0.5, 0.4)
        glEnd()
      DispList:endList()
   end
\end{Verbatim}

There is one problem with the new \code{make\_the\_thing()}: if a display list
for {\em myobject} already exists, the function will not be executed and the
object will keep its current shape. This can be fixed if user closes and
reopens the OpenGL view which will create a new OpenGL context. A better
approach is to use a global variable with a list of display list names that
have to be recreated. We change \code{initlists()} so that it verifies if any
objects should be deleted.
\todo{VERIFY: code from this point on is not verified}

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   renewal = {} 
   function initlists()
      if #renewal > 0 then
         local ren = renewal; renewal = {}
         for _,name in pairs(ren) do DispList:delete(name) end
      end
      if not DispList:exists('myobject') then make_the_thing() end
   end
\end{Verbatim}

When we define a new version of \code{make\_the\_thing()} we add the name of
the display list to be recreated ({\em myobject}) to the \code{renewal} table:

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   function make_the_thing()
      ...
   end
   table.insert(renewal, 'myobject')
\end{Verbatim}

>>>>

Chunks for the head and the body part of a document are independent. This means
that a chunk in the head may have the same partId as a chunk in the body of
a document. When a part is removed from a document, the chunks for the head
and the body with the requested partId are removed.
\todo{TODO: ICE interface for removing (parts of) objects is still missing}

@@

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   DispList:newList(name)
   DispList:endList()
   DispList:delete(name)
   DispList:exists(name)
   DispList:draw(name)
   DispList:setDirty(name)
   DispList:getDirty(name_table)
\end{Verbatim}

@@

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   function make_the_thing()
      DispList:newList('myobject')
        glBegin(GL_TRIANGLES)
        glVertex(0.1, 0.1, 0.1)
        glVertex(0.3, 0.1, 0.2)
        glVertex(0.3, 0.4, 0.3)
        glEnd()
      DispList:endList()
   end

   function initlists()
      local dirty = DispList:getDirty( {'myobject'} )
      if dirty['myobject'] then
         make_the_thing()
      end
   end

@@

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   function make_the_thing()
      DispList:create('myobject')
        glBegin(GL_QUADS)
        glVertex(0.1, 0.1, 0.1)
        glVertex(0.3, 0.1, 0.2)
        glVertex(0.3, 0.4, 0.3)
        glVertex(0.0, 0.5, 0.4)
        glEnd()
      DispList:endList()
   end
   DispList:setDirty('myobject')
\end{Verbatim}

The function \code{setDirty()} tells the display list manager that the object
was modified. The renderer will detect the change the next time
\code{getDirty()} is called, in this case from \code{initlists()}.
\code{getDirty(namelist)} returns a table with keys that represent the names of
the objects from {\em namelist} that need to be recreated. It will contain the
names of the objects that were not yet created and the objects that were marked
as dirty. The list of dirty objects is reset after every call to
\code{getDirty()}.

The module \code{StdModel} defines the following functions that create simple shapes:

\begin{Verbatim}[fontsize=\scriptsize,gobble=3]
   StdModel:box(sx, sy, sz)
   StdModel:cylinder(rx, ry, np)
\end{Verbatim}

The box and the cylinder are created with the center in $(0, 0, 0)$. The
parameters for the box define the size of the box. The cylinder has an elliptic
shape with the given radii and is approximated with {\em np} sides.
